% Chapter 5

\chapter{Project Planning And Work Achieved} % Main chapter title

\label{Chapter5} % For referencing the chapter elsewhere, use \ref{Chapter1} 

%----------------------------------------------------------------------------------------

% Define some commands to keep the formatting separated from the content 
%\newcommand{\keyword}[1]{\textbf{#1}}
%\newcommand{\tabhead}[1]{\textbf{#1}}
%\newcommand{\code}[1]{\texttt{#1}}
%\newcommand{\file}[1]{\texttt{\bfseries#1}}
%\newcommand{\option}[1]{\texttt{\itshape#1}}

%----------------------------------------------------------------------------------------

\section{Project Planning}

\paragraph At the beginning of the project, a planning was requested with the main tasks to be done and the estimated efforts for each one. Table \ref{tab:planning} shows this planning as well as the actual effort needed for each task.

\begin{table}[htbp]
	\centering
		\begin{tabular}{| m{7em} | m{7cm}| m{2cm} | m{1cm} |} 
		 \hline
		 \textbf{Task}            & \textbf{Description}                                    & \textbf{Estimation} & \textbf{Actual} \\
		 \hline
		 Application Development  & Coding of the application, including learning Spring FW & 5h                  & 10h \\ 
		 \hline
		 Features Definition      & Writing of the features in Gherkin format               & 5h                  & 5h  \\ 
		 \hline
		 Test Step Implementation & Coding of the test steps until they all pass            & 20h                 & 10h \\
		 \hline
		 Pipeline: Docker         & Docker learning, creation of the images and coding      & 20h                 & 15h \\
		 \hline
		 Pipeline: Other jobs     & Maven build and test jobs (only triggering)             & 5h                  & 5h \\
		 \hline
		 Report                   & This document                                           & 5h                  & 10h \\ [1ex] 
		 \hline
		\end{tabular}
	\caption{Planning and Efforts}
	\label{tab:planning}
\end{table}

\paragraph While there has been a difference between the expected most time consuming tasks and the actual ones, the total amount of hours dedicated to the project more or less match with the initial estimation. Is noticeable the amount of time dedicated to application development and this report which in both cases the initial estimation has been doubled. However, the extra amount of time needed for those tasks has been compensated with the significant less time needed for test step implementation and pipeline tasks.
 
%----------------------------------------------------------------------------------------

\section{Work Achieved}

If compared with the project objectives in chapter \ref{Chapter1}, the work achieved at the end of the project fits with those objectives. From a practical point of view some of the test steps were left without implementation but the objective behind can be considered as accomplished. In the same direction, the number of features written could have been much larger, including the Component test level, but it would have not added any value to the project objectives as a real test of the application is out of the scope of the project.

